Redshift evolution of the SN stretch distribution

### 2019-11-21 Nicolas.tex
First draft of mag-limited zmax

The simple use of those is not enough for our aim, as SNe Ia have an intrinsec
dispersion of their luminosity of $\approx 0.4~mag$ that gives a huge
uncertainty on the determination of their distance modulus. Henceforth they are
standardized using the "brigther-slower" and "brighter-bluer" relations
(Philipps 93, Riess 96, Tripp 98) in the SALT2 algorithm (Guy 2007, 2010) that
fits the distance modulus which is expressed as
\begin{equation}
    \m = m_b + \a x_1 - \b c - M
\end{equation}
with $m_B$ the logarithm of their flux, $x_1$ their stretch, $c$ their color and
$M$ their intrinsec magnitude. This relation lowered their magnitude dispersion
to $\approx 0.15~mag$, allowing for previously mentioned accelerated
expansion to be discovered.

@@

We use data from 5 different surveys: Hubble Space Telescope (HST, REF),
Supernova Nearby Factory (SNf, REF), Supernova Legacy Survey (SNLS, Aster 2006,
Betoule 2014), Sloan DSS (SDSS, REF) and Panstarr-1 (PS1, REF). The last 3 had
selection effects that come from the "brighter-slower" and "brighter-bluer"
relations: the first SNe Ia that are missed by the instruments are the redder
and faster ones. That implies that taking all of these surveys' data would not
represent the stretch distribution that Nature could give us.

>>>>

The simple use of those is not enough for our aim, as SNe Ia have an intrinsec
dispersion of their luminosity of $\approx 0.4~mag$ that gives a huge
uncertainty on the determination of their distance modulus. Henceforth they are
standardized using the "brigther-slower" and "brighter-bluer" relations
(Philipps 93, Riess 96, Tripp 98) in the SALT2 algorithm (Guy 2007, 2010) that
fits the distance modulus which is expressed as
\begin{equation}\label{eq:tripp}
    \m = m_b + \a x_1 - \b c - M
\end{equation}
with $m_B$ the logarithm of their flux, $x_1$ their stretch, $c$ their color and
$M$ their intrinsec magnitude. This relation lowered their magnitude dispersion
to $\approx 0.15~mag$, allowing for previously mentioned accelerated
expansion to be discovered.

@@

We use data from 5 different surveys: Hubble Space Telescope (HST, REF),
Supernova Nearby Factory (SNf, REF), Supernova Legacy Survey (SNLS, Aster 2006,
Betoule 2014), Sloan DSS (SDSS, REF) and Panstarr-1 (PS1, REF). The last 3 had
selection effects that come from the "brighter-slower" and "brighter-bluer"
relations: the first SNe Ia that are missed by the instruments are the redder
and faster-declining ones. That implies that taking all of these surveys' data
would not represent the stretch distribution that Nature could give us.

We used the 5$\sigma$ depth of each survey to know what was the smallest
apparent magnitude they could acquire. We want to find the maximum redshift
(or equivalently distance modulus assuming Planck15 cosmology) for which all
combination of stretch and color are visible. We computed the absolute magnitude
5 days prior peak (taken at $-19.3\,$mag) for each value of
$(x_1, c)$ in an $([-3, 3], [-0.3, 0.3])$ ellipse, finding which combination had
the smallest one, using a SALT2 model in SNCosmo. Using $\a$ and $\b$ given in
Scolnic 2018a, we can then compute the distance modulus corresponding to that
minimum absolute magnitude and verifying \eqref{eq:tripp}.
